Synthesizing Symmetric Lenses

### 2018-07-10 papers/SymmetricLenses/main.tex
finished pass over abstract

Synthesizing simple symmetric lenses is substantially more challenging that
synthesizing bijective lenses: since some of the information on each side
can be ``disconnected'' from the other side, there will in general be {\em
  many} lenses that agree with a given example.  To guide the search
process, we use {\em stochastic regular expressions} and ideas from
information theory to estimate the amount of information propagated by a
candidate lens.

We describe an implementation of simple symmetric lenses and our synthesis
procedure as extensions to the Boomerang language~\cite{Boomerang} and evaluate
its performance on a range of benchmark examples. We find this implementation is
able to synthesize all the lenses of this benchmark suite in under 30 seconds.
\end{abstract}

>>>>

Synthesizing simple symmetric lenses is substantially more challenging that
synthesizing bijective lenses: Since some of the information on each side
can be ``disconnected'' from the other side, there will in general be {\em
  many} lenses that agree with a given example.  To guide the search
process, we use {\em stochastic regular expressions} and ideas from
information theory to estimate the amount of information propagated by a
candidate lens.

We describe an implementation of simple symmetric lenses and our synthesis
procedure as extensions to the Boomerang language~\cite{Boomerang}. We
evaluate
its performance on 45 benchmark examples drawn from FlashFill, Augeus,
and an online collection of electronic file formats. We find this implementation is
able to synthesize all the lenses of the benchmark suite in under 30 seconds.
\end{abstract}
